R Python, and Ruby clients for GBIF species occurrence data

### 2017-09-07 manuscript.Rmd
changes

Both R and Python are commonly used in science, and can be used for similar
tasks. Python, however, is a more general programming lanugae, and can be
used in more contexts than R can be used in.

The `rgbif` and `pygbif` clients can do a lot of the same tasks. We
envision `rgbif` as being more common in workflows of academics asking
research questions, whereas `pygbif` can do that as well, but may be more
easily used in a website.

The R client `rgbif` has much more development time than `pygbif`,
but through time `pygbif` will become equally mature.

>>>>

Both R and Python are commonly used in science, and can be used for similar
tasks. Python, however, is a more general programming lanugae, and can be
used in more contexts than R can be used in. Ruby is used very little in
science; but, like Python, Ruby is very widely used as a general purpose
programming language, with heavy use in web development and web services.

The three clients can do a lot of the same tasks. We envision `rgbif`
being more common in workflows of academics asking research questions,
whereas `pygbif` and `gbifrb` can do that as well, but may be more easily
used in a website.

The R client `rgbif` has had much more development time than `pygbif`
and `gbifrb`, but with time `pygbif` and `gbifrb` will become equally
mature.
